\pdftitle

### 2017-05-14 maxNt.tex
Complete intro

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2017-05-13T17:24:25+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

%\newcommand*{\delt}{\deltaup}%Kronecker, Dirac

@@

%\newcommand*{\defs}{\eqqcolon}

@@

%\newcommand*{\labelbis}[1]{\tag*{(\ref{#1})$_\text{r}$}}

@@

\newtheoremstyle{simple}%
{0\parsep}%
{0\parsep}%
{\footnotesize}%
{}%
{}%
{}%
{0pt}%
{}%
\theoremstyle{simple}
\newtheorem*{simplenote}{}

@@

\newcommand*{\av}{\widebar} %pop average
\newcommand*{\sav}{\widehat} %subpop average

\newcommand*{\yxx}{x}%subpop state
\newcommand*{\yx}{\bm{\yxx}}%subpop state
\newcommand*{\yxs}{\sav{\yx}}%subpop av state
\newcommand*{\yxxs}{\sav{\yx\yx}}%subpop av state
\newcommand*{\yX}{\bm{X}}%pop state
\newcommand*{\yXf}{\av{\yX}}%pop av state
\newcommand*{\yr}{\bm{r}}%subpop value
\newcommand*{\yrs}{\sav{\yr}}%subpop av value
\newcommand*{\yR}{\bm{R}}%pop value
\newcommand*{\yRf}{\av{\yR}}%pop av value
%conditional assumptions
\newcommand*{\yH}{\varEta}
\newcommand*{\yD}{\varDelta}
\newcommand*{\yHa}{\varEta'}
\newcommand*{\yHb}{\varEta''}
%Lagr multipliers
\newcommand*{\yL}{\varLambda}
\newcommand*{\yl}{\lambda}
\newcommand*{\yk}{\kappa}
%entropies
\newcommand*{\ysh}{H}
\newcommand*{\ybu}{H_{\text{B}}}

@@

@@

Maximum-entropy models are used for a variety of (sometimes not completely
clear) reasons. For our purposes let's say that the \me\ method is assumed
to generate a \enquote{maximally noncommital} \cite{jaynes1963} probability
distribution. We intend the quoted expression only as an umbrella term,
also because it means very little without further clarifications.

The neurons recorded in these kinds of experiments are usually picked out
in a way beyond our control, and from their observation we expect to learn
something about all other neurons in the same brain area. That is, they are
assumed to be a \enquote{representative random sample} of the neurons in
that area. Our discussion hinges on this often just tacitly understood
assumption.

@@

Consider a population of $N$ binary neurons with states $(X_1,\dotsc,X_N)$
having fixed but unknown binary values $(R_1,\dotsc,R_N)$, with
$R_i \text{ in } \set{0,1}$, vectorially written $\yX=\yR$. For example,
$\yX$ can represent the state of a population at a particular time. We call
the neurons \enquote{units} to lend some generality to our discussion. We
shall make statements about the whole population of $N$ units and about a
subpopulation of $n$ units; the word \enquote{population} will always refer to
the \emph{whole} population. The subpopulation states and their values are
denoted by lowercase letters: $(x_1, \dotsc, x_n)\equiv\yx$ and
$(r_1, \dotsc, r_n)\equiv\yr$; but note that $x_i \equiv X_{j_i}$ and
$r_i \equiv R_{j_i}$ for some distinct $j_1,\dotsc,j_n$. We shall also make
statements about the population-averaged state, or \emph{population average}:
\begin{align}
  \label{eq:population-av}
   \yXf &\defd (X_1 + \dotsb + X_N)/N,
\\
\intertext{and the subpopulation-averaged state, or \emph{subpopulation average}:}
\label{eq:subpopulation-av}
\yxs &\defd (x_1 + \dotsc + x_n)/n.
\end{align}
The quantities $N\yXf$ and $n\yxs$ represent the total number of active
units in the population and the subpopulation. Quantities like $\yRf$ and $\yrs$
are defined analogously. The averaging operators $\sav{\dotv}$ and
$\av{\dotv}$ are also extended to averages of $\tbinom{n}{m}$ or
$\tbinom{N}{m}$ products of $m$ states; \eg,
\begin{align}
\av{\yX \yX} &\defd
\tbinom{N}{2}^{-1} (X_1 X_2 + X_1 X_3  + \dotsb +  X_{N-1} X_N),
\\[2\jot]
\sav{\yx\yx\yx} &\defd
\tbinom{n}{3}^{-1} (x_1 x_2 x_3 + x_1 x_2 x_4 + \dotsb + x_{n-2} x_{n-1} x_n),
\end{align}
and so on.

@@

>>>>

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2017-05-14T12:06:05+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

\newcommand*{\delt}{\deltaup}%Kronecker, Dirac

@@

\newcommand*{\defs}{\eqqcolon}

@@

\newcommand*{\labelbis}[1]{\tag*{(\ref{#1})$_\text{r}$}}

@@

\newtheoremstyle{simple}%
{}%.5\baselineskip plusminus.2\baselineskip % \parsep
{}%
{\footnotesize}%
{}%
{}%
{}%
{0pt}%
{}%
\theoremstyle{simple}
\newtheorem*{simplenote}{}

@@

\newcommand*{\av}{\widebar} %pop average
\newcommand*{\sav}{\widebar} %subpop average

\newcommand*{\yxx}{x}%subpop state
\newcommand*{\yx}{\bm{\yxx}}%subpop state
\newcommand*{\yxs}{\sav{\yx}}%subpop av state
\newcommand*{\yX}{\bm{X}}%pop state
\newcommand*{\yy}{\bm{y}}%pop state
\newcommand*{\yXf}{\av{\yX}}%pop av state
\newcommand*{\yxxs}{\sav{\yx\yx}}%subpop av state
\newcommand*{\yXXf}{\av{\yX\yX}}%subpop av state
\newcommand*{\yr}{\bm{r}}%subpop value
\newcommand*{\ys}{\bm{s}}%subpop value
\newcommand*{\yrs}{\sav{\yr}}%subpop av value
\newcommand*{\yR}{\bm{R}}%pop value
\newcommand*{\yRf}{\av{\yR}}%pop av value
%conditional assumptions
\newcommand*{\yH}{\varEta}
\newcommand*{\yD}{\varDelta}
\newcommand*{\yHa}{\varEta'}
\newcommand*{\yHb}{\varEta''}
%Lagr multipliers
\newcommand*{\yL}{\varLambda}
\newcommand*{\yl}{\lambda}
\newcommand*{\yk}{\kappa}
%entropies
\newcommand*{\ysh}{H}
\newcommand*{\ybu}{H_{\text{B}}}

@@

The present note has three nested purposes.

The first and more general is to remind our readers that the \me\ method
rests on subtle assumptions that may be contradictory with other
assumptions we want to make on the data under study.

As a concrete example we show -- and this is the second purpose -- that a
sample of a neuronal population cannot be assigned a \enquote{maximally
  noncommittal} \me\ distribution and at the same time be considered a
\enquote{random representative} of the population.

The proof of the example above rests on some probability relations from
classical random sampling. These relations are somewhat hard to find
explicitly stated in the neuroscientific literature; the third, minor
purpose of this note is to state them explicitly.

@@

Maximum-entropy models are used for a variety of (sometimes not completely
clear) reasons. For our purposes let's say that the \me\ method is assumed
to generate a \enquote{maximally noncommittal} \cite{jaynes1963} probability
distribution. We intend the quoted expression only as an umbrella term,
also because it means very little without further clarifications.

The neurons recorded in these kinds of experiments are usually picked out
according to an unknown process, and from their observation we expect to
learn something about all other neurons in the same brain area. That is,
they are assumed to be a \enquote{representative random sample} of the
neurons in that area. Our discussion hinges on this often just tacitly
understood assumption.

@@

We have a population of $N$ binary neurons. Let's assume that the
identities of the neurons can be distinguished, by their spike shapes for
example; but other details, like their locations, are unknown. The neurons
have a joint state $(X_1,\dotsc,X_N) \defs \yX$ having fixed but unknown
binary values $(R_1,\dotsc,R_N)\defs \yR \in \set{0,1}^N$. A particular
sample of $n$ neurons from this population has joint state
$(x_1, \dotsc, x_n) \defs \yx$ having fixed binary values
$(r_1, \dotsc, r_n)\defs\yr$. We will consider various averages for the
population and the sample. For this purpose we introduce a general
averaging operator $\sav{\dotv}$ defined by
\begin{align}
  \av{\yX}  &\defd \tfrac{1}{N} (X_1 + X_2 + \dotsb + X_N),
  &
  \sav{\yx}  &\defd \tfrac{1}{n} (x_1 + x_2 + \dotsb + x_n),
    \\[2\jot]
  \av{\yX \yX} &\defd
\tbinom{N}{2}^{-1} (X_1 X_2 + X_1 X_3  + \dotsb +  X_{N-1} X_N),
  &
    \sav{\yx \yx} &\defd
\tbinom{n}{2}^{-1} (x_1 x_2 + x_1 x_3  + \dotsb +  x_{n-1} x_n),
\\[2\jot]
\av{\yX\yX\yX} &\defd
                  \tbinom{N}{3}^{-1}
                  (X_1 X_2 X_3 +% X_1 X_2 X_4
                   \dotsb + X_{N-2} X_{N-1}X_N),
  &
    \sav{\yx\yx\yx} &\defd
                      \tbinom{n}{3}^{-1} (x_1 x_2 x_3 + %x_1 x_2 x_4
                       \dotsb + x_{n-2} x_{n-1} x_n),
\end{align}
and so on; analogously for the quantities $\yR$ and $\yr$. These formulae
say that $\yXf$ is the fraction of active neurons, $\yXXf$ the fraction of
simultaneously active pairs out of all $\binom{N}{2}$ pairs, $\av{\yX\yX\yX}$
the fraction of simultaneously active triplets, and so on.

\begin{simplenote}
  A sample can be \enquote{random} in two different ways. Consider the
  population of neurons named $\set{1,2,3}$ for example. The sample
  $\set{1,3}$ is random because neurons $1$ and $3$ were chosen according
  to an unknown process. The sample $\set{\textrm{X}_1, \textrm{X}_2}$ is
  random because we don't know the identity of neurons $\textrm{X}_1$ and
  $\textrm{X}_2$. Given the probability for the population, the
  probabilities for the states of these two samples are different: the
  former is obtained by marginalization, the latter by symmetrization and
  marginalization.
\end{simplenote}

Our uncertainty about the state of the population is completely expressed by the
probability distribution
\begin{equation}
  \label{eq:joint_plaus}
  \p(X_1=R_1, X_2=R_2, \dotsc, X_N=R_N \| \yH) \quad\text{or}\quad
\p(\yX =\yR \| \yH), \quad \yR \in \set{0,1}^N,
\end{equation}
where $\yH$ denotes our state of knowledge (the evidence and assumptions
backing our probability assignments). Our uncertainty about the state of
the sample is likewise expressed by
\begin{equation}
  \label{eq:sample_plaus}
  \p(x_1=r_1, x_2=r_2, \dotsc, x_n=r_n \| \yH) \quad\text{or}\quad
\p(\yx =\yr \| \yH), \quad \yr \in \set{0,1}^n.
\end{equation}

\subsection{Initial assumptions}
\label{sec:initial_assumptions}

Before any experimental observations are made we need to make an initial
probability assignment, no matter what kinds of predictions we are
interested in. This initial assignment will be modified by the experimental
observations.

We yet know very little about the physical details of the individual
neurons, like their locations. Our state of knowledge is therefore
symmetric, or \enquote{exchangeable}, under their permutations. This
symmetry must be reflected in our initial probability, and the
\emph{representation theorem for finite exchangeability} states that it
must obey
\begin{equation}
  \label{eq:joint_plaus_N_homog}
  \p(\yX = \yR \| \yH) = \binom{N}{N\yRf}^{-1} \p(\yXf=\yRf \| \yH),
\end{equation}
the latter being the probability for the population average $\yX$. Proof
and generalizations to non-binary and continuum cases are given by
de~Finetti \cite{definetti1959b}, Ericson \cite{ericson1976}, Diaconis
\cite{diaconis1977}, Heath \amp\ Sudderth \cite{heathetal1976}. This
theorem is intuitive: owing to symmetry, all states with $N\yRf$ active
neurons must have equal probabilities.

By marginalization we obtain the probability for the state of the sample:
\begin{gather}
  \label{eq:marginal}
  \p(\yx = \yr \| \yH) = \binom{n}{n\yrs}^{-1} \p(\yxs=\yrs \| \yH),
  \\
  \shortintertext{with}
  \label{eq:subpop_average}
  \p(\yxs=\yrs \| \yH) = \binom{n}{n\yrs}
  \sum_{N \yRf =0}^{N} \binom{N-n}{N \yRf-n\yrs}\binom{N}{N \yRf}^{-1}\,
  \p(\yXf=\yRf \| \yH).
\end{gather}
The combinatorial proof is the same as for the theory of drawing without
replacement, leading to the hypergeometric distribution, and can be found
in many texts
\cites[\chap~3]{jaynes1994_r2003}[\sect~4.8.3]{ross1976_r2010}[\sect~II.6]{feller1950_r1968}.
The symmetry of our initial ignorance should intuitively also apply to the
sample. This is indeed the case: the probability for the state of the
sample~\eqref{eq:subpop_average} automatically satisfies the representation
theorem~\eqref{eq:joint_plaus_N_homog} as well.

Formula~\eqref{eq:subpop_average}, connecting our initial probabilities for
the population and sample averages, has a very important consequence: \emph{our
expectations for all averages of the sample and the full population are the
same}:
\begin{multline}
  \label{eq:expe_products}
\expe{\sav{\underbrace{\yx \dotsm \yx}_{\text{$m$ factors}}} \| \yH}
=
\expe{\av{\underbrace{\yX \dotsm \yX}_{\text{$m$ factors}}} \| \yH}
\\[2\jot]
{}=\sum_{N \yRf=0}^N %m!\, 
\binom{N-m}{N \yRf-m}
\binom{N}{N \yRf}^{-1} \p(\yXf=\yRf \| \yH)
\equiv
\binom{N}{m}^{-1}
%\frac{(N-m)!}{N!}
\sum_{N \yRf=0}^N %m!\, 
\binom{N \yRf}{m}\, \p(\yXf=\yRf \| \yH).
\end{multline}

\iffalse
\begin{align}
  \expe{x_{i_1} \dotsm x_{i_m} \| \yH}
&=
\expe{\sav{\underbrace{\yx \dotsm \yx}_{\text{$m$ factors}}} \| \yH}
=
\expe{\av{\underbrace{\yX \dotsm \yX}_{\text{$m$ factors}}} \| \yH},
\\
\intertext{and has an explicit expression in terms of $Q$:}
  \begin{split}
\expe{x_{i_1} \dotsm x_{i_m} \| \yH}
&=
\binom{N}{m}^{-1}
%\frac{(N-m)!}{N!}
\sum_{N A=0}^N %m!\, 
\binom{N A}{m}\, Q(A)
\\
&\equiv
%\frac{(N-m)!}{N!}
\sum_{N A=0}^N %m!\, 
\binom{N-m}{N A-m}
\binom{N}{N A}^{-1} Q(A).
\end{split}
\end{align}
\end{subequations}
\fi
***

What do we mean by saying that we can learn something about the population
by observing the sample? At the very least we mean that our uncertainty
about the rest of the population can change upon observing the sample. That
is, the probability for the state $\yy$ of the rest of the population is
conditionally dependent on the sample's values:
\begin{equation}
  \label{eq:conditionally_dependent_sample}
  \p(\yy =\ys \| \yx=\yr,\yH) \ne \p(\yy =\ys \|\yH)
  \qquad\text{for some $\ys,\yr$},
\end{equation}
This also means that the probability for the population cannot be
factorized into that of the sample times that of the complement.

What do we mean when we say that the sample is representative of the
population? It means that we expect some collective properties of the
sample, like the fraction of active neurons, or the fraction of
simultaneously active pairs, to be roughly equal to those of the full
population.

For example, $\yX$ can
represent the state of a population at a particular time. We call the
neurons \enquote{units} to lend some generality to our discussion. We shall
make statements about the whole population of $N$ units and about a
subpopulation of $n$ units; the word \enquote{population} will always refer
to the \emph{whole} population. The subpopulation states and their values
are denoted by lowercase letters: $(x_1, \dotsc, x_n)\equiv\yx$ and
$(r_1, \dotsc, r_n)\equiv\yr$; but note that $x_i \equiv X_{j_i}$ and
$r_i \equiv R_{j_i}$ for some distinct $j_1,\dotsc,j_n$. We shall also make
statements about the population-averaged state, or \emph{population
  average}:
\begin{align}
  \label{eq:population-av}
   \yXf &\defd (X_1 + \dotsb + X_N)/N,
\\
\intertext{and the subpopulation-averaged state, or \emph{subpopulation average}:}
\label{eq:subpopulation-av}
\yxs &\defd (x_1 + \dotsc + x_n)/n.
\end{align}
The quantities $N\yXf$ and $n\yxs$ represent the total number of active
units in the population and the subpopulation. Quantities like $\yRf$ and $\yrs$
are defined analogously. The averaging operators $\sav{\dotv}$ and
$\av{\dotv}$ are also extended to averages of $\tbinom{n}{m}$ or
$\tbinom{N}{m}$ products of $m$ states; \eg,
\begin{align}
\av{\yX \yX} &\defd
\tbinom{N}{2}^{-1} (X_1 X_2 + X_1 X_3  + \dotsb +  X_{N-1} X_N),
\\[2\jot]
\sav{\yx\yx\yx} &\defd
\tbinom{n}{3}^{-1} (x_1 x_2 x_3 + x_1 x_2 x_4 + \dotsb + x_{n-2} x_{n-1} x_n),
\end{align}
and so on.

@@

  \section{Sketched proofs}
  \label{sec:derivations}

  Variants of the following derivations and combinatorial considerations
  can be found \eg\ in
  \cites[\chaps~I--IV]{whitworth1867_r1965}[\chap~II]{feller1950_r1968}[\chap~3]{jaynes1994_r2003};
  see also \citep{whitworth1897}.

  To derive the joint probability distribution
  \eqref{eq:joint_plaus_N_homog} from that for the network
  average~\eqref{eq:pop_average_Q}, consider that if the network total
  is $N\yXf$, then $N\yXf$ out of $N$ units are active, and there are
  $\tbinom{N}{N\yXf}$ possible states for which this can be true; therefore
  \begin{equation}
    \labelbis{eq:joint_plaus_N_homog}
    \p(\yX = \yR \| H) = \binom{N}{N\yRf}^{-1}Q(\yRf).
  \end{equation}
An analogous reasoning for $n$ and $\yxs$ leads to an analogous equality,
\begin{equation}
  \label{eq:aver_subpop}
  \p(\yx=\yr \| H) = \binom{n}{n\yrs}^{-1} \p(\yxs=\yrs\|\yH),
\end{equation}
for the subnetwork.

Let us next consider the probability $\p(\yxs =a \| \yXf = A,\yH)$ for
the subnetwork average $\yxs$ conditional on the network average $\yXf$.
There are $\tbinom{N}{N\yXf}$ possible network states if the network
average is $\yXf$, \ie\ if $N\yXf$ units are in state $1$; the conditional
probability of each is therefore $1/\tbinom{N}{N\yXf}$, owing to the
symmetry assumption~\eqref{eq:homog_math}. Now consider the subnetwork of the
first $n$ units. The conditional probability of having $n\yxs$ specific
ones in state $1$ is the sum of the probabilities of all states for
which $N\yXf-n\yxs$ of the remaining $N-n$ units are in state $1$; there are
$\tbinom{N-n}{N\yXf-n\yxs}$ such states, all equally probable. Finally,
there are $\tbinom{n}{n\yxs}$ possible ways, all equally probable, in which
$n\yxs$ of the first $n$ units can be in state $1$. In formulae,
\begin{equation}
\label{eq:conditional_prob_explained}
\begin{split}
      \p(\yxs =a \| \yXf=A, \yH)
      &=
      \sum_{\yr}^{\yrs=a} \sum_{\yR}^{\yRf=A} 
      \p(\yx =\yr \|  \yX = \yR, \yH) \,
      \p(\yX =\yR  \| \yXf=A,\yH),
      \\
      &=
      \sum_{\yr}^{\yrs=a} \sum_{\yR}^{\yRf=A} 
      \p(\yx=\yr \|  \yX =\yR, \yH) \,
      \binom{N}{N A}^{-1},
      \\
      &=\sum_{\yr}^{\yrs=a} 
      \binom{N-n}{N A-n a}\binom{N}{N A}^{-1},
      \\
      &=
      \binom{n}{n a}\binom{N-n}{N A-n a}\binom{N}{N A}^{-1},
\end{split}
\end{equation}
  which is the conditional probability~\eqref{eq:conditional_prob}. Note
  that this is just a derivation of the hypergeometric distribution
  \cites[\chap~3]{jaynes1994_r2003}[\sect~4.8.3]{ross1976_r2010}[\sect~II.6]{feller1950_r1968},
  which describes the probability of, say, drawing a proportion of $\yxs$
  blue balls in $n$ drawings without replacement from an urn with $N$
  balls, a fraction $\yXf$ of which are blue.

  \bigskip The probability of a subnetwork average $\yxs$ is then, by
  marginalization,
  \begin{equation}
    \label{eq:subpop_average_explained}
    \begin{split}
      \p(\yxs =a \| \yH)
      &= \sum_{N A=0}^N\p(\yxs = a \| \yXf = A, \yH)\,
      \p(\yXf = A \| \yH),
      \\
      &=\sum_{N A=0}^N
      \binom{n}{n a}\binom{N-n}{N A-n a}\binom{N}{N A}^{-1}
      Q(A).
    \end{split}
  \end{equation}
  which proves the subnetwork-average formula~\eqref{eq:subpop_average}.
  This formula, combined with \eqns~\eqref{eq:aver_subpop} and
  \eqref{eq:joint_plaus_N_homog}, leads to the conditional
  probability~\eqref{eq:conditional_total_state}.

  \bigskip The independence of the expectation of products of states from
  the subnetwork size is trivial by marginalization:
  \begin{multline}
    \label{eq:margin_products}
    \sum_{\yx} x_1\dotsm x_m \p(\yx =\yr \| \yH)
      =\sum_{\yr,\yR}  r_1\dotsm r_m \p(\yx=\yr \| \yX=\yR,\yH)
      \, \p(\yX=\yR \| \yH),
      \\
      \begin{aligned}
      &=\sum_{\yr,\yR} r_1\dotsm r_m\,\delt(R_1-r_1)\dotsm\delt(R_m-R_m)
      \p(\yX = \yR \| \yH),
      \\
      &=\sum_{\yR} R_1\dotsm R_m \p(\yX =\yR \| \yH).
    \end{aligned}
  \end{multline}
  All such $m$-fold products have the same expectation by symmetry,
  therefore their subnetwork average will do, too, being an average of
  equal terms.

  Now consider the sum of all distinct products of states of two units in
  the subnetwork:
  \begin{equation*}
    x_1 x_2 + x_1 x_3 + \dotsb + x_{n-1} x_n.
  \end{equation*}
  The terms in this sum are either $0$ or $1$. The non-vanishing ones are
  those with index pairs chosen from the $n\yxs$ units of the subnetwork
  which are in state $1$, and there are $\tbinom{n\yxs}{2}$ such choices,
  so the sum above is equal to $\tbinom{n\yxs}{2}$. The sum has
  $\tbinom{n}{2}$ terms, so their average is
  $\tbinom{n\yxs}{2}/\tbinom{n}{2}$. Generalizing the argument to products
  of $m$ units, we have that
  \begin{equation}
    \sav{x_{i_1} \dotsm x_{i_m}} = \binom{n\yxs}{m} \binom{n}{m}^{-1}.
  \end{equation}
  Then, using \eqn~\eqref{eq:subpop_average},
  \begin{multline}
    \label{eq:expect_product_m}
    \expe*{\sav{x_{i_1} \dotsm x_{i_m}} \| \yH}
    \\
    \begin{aligned}[b]
      &=\tfrac{(n-m)!}{n!}
      \expe*{m!\,\tbinom{n\yxs}{m}  \| \yH}
      \\
      &\equiv\frac{(n-m)!}{n!}
      \sum_{n a=0}^n m!\, \binom{n a}{m} \p(\yxs =a \|\yH),
      \\
      &=\frac{(n-m)!}{n!} \sum_{N A=0}^N
      Q( A)
      \Biggl[ 
      \sum_{n a=0}^n 
      m!\,\binom{n a}{m}\, \binom{n}{n a}\binom{N-n}{N A-n a}\binom{N}{N A}^{-1} 
      \Biggr].
    \end{aligned}
  \end{multline}
  The expression in brackets is the $m$th factorial moment of the
  hypergeometric function, and is given by \citep{potts1953}
%file: factorial_moments_etc.nb
  \begin{equation}
    \sum_{n a=0}^n m!\,\binom{n a}{m} \binom{n}{n a}\binom{N-n}{N\yXf-n a}
    \binom{N}{N\yXf}^{-1} 
    =
    m!\,\binom{n}{m} \binom{n a}{m}\binom{N}{m},
  \end{equation}
  which combined with the previous equation yields the second line of
  \eqn~\eqref{eq:expe_products}; its last equality comes from the identity
  \begin{equation}
    \label{eq:binom_identity}
    \binom{N}{M}\binom{M}{m}=\binom{N}{m}\binom{N-m}{M-m},
  \end{equation}
  easily derived by writing the binomial coefficients in terms of
  factorials. Finally, \eqns~\eqref{eq:moments}, relating the moments of
  the distributions for subnetwork and network averages, is obtained
  from the definition of moments,
  \begin{equation}
    \label{eq:moments_def}
    \expe*{\yxs^m \| \yH} \defd
    \sum_{n a=0}^{n} a^m \p(\yxs = a  \| H),
    \quad
    \expe{\yXf^m \| \yH} \defd
    \sum_{N A=0}^{N} A^m \p(\yXf = A  \| H),
  \end{equation}
  replaced in the equalities for the factorial
  moments~\eqref{eq:eq_factmom_prod}, by recursively solving in terms of
  the moments of the network distribution.
